Utilizing Convolution for Obstacle Avoidance during Robotic Manipulator Movement

### 2023-07-21 Articles/ERK/erk.tex
ERK article
ERK added color main axis scheme
Update erk.tex
ERK minor
ERK citat 1

Robotic manipulators, specifically those with a high degree of freedom (DOF), possess a crucial characteristic known as kinematic redundancy. Kinematic redundancy refers to having more joints (i.e., degrees of freedom - DOF) than required to perform a task, thus allowing the robot to adopt multiple configurations to accomplish the same end-effector position and orientation. This redundancy provides a considerable advantage, making it possible for manipulators to optimize movement according to different criteria, such as energy efficiency, obstacle avoidance, or joint limit avoidance.

@@

Geometric kinematics (also known as forward and inverse kinematics) focuses on the relationship between joint angles and the position and orientation of the end-effector. Forward kinematics involves calculating the position and orientation of the end-effector given the joint angles, while inverse kinematics is the process of determining the joint angles for a desired end-effector position and orientation. In the case or redundant manipulator, there isn't an unique mapping from EE coordinates to the joint coordinates. as there are exist an infinite number of different joint angles that can map to the same EE position.

Differential kinematics, also known as the Jacobian analysis, forms the foundation of robot velocity analysis. The Jacobian matrix, often represented as $J$, encapsulates the relationship between the joint velocities and the end-effector linear and angular velocities. It's derived from the partial derivatives of the forward kinematics.

@@

\todocomment{IMAGE OF FILTERS}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\linewidth]{kernel-mainvalues.png}
	\caption{The kernel values along the primary axis exhibit a pattern of symmetrical distribution with negative polarity on one side.} 
	\label{Kernel main axis}
\end{figure}

@@

@@

\bibitem{ERK} ERK, http://www.ieee.si/erk/index.html 
\bibitem{Zbornik} B. Zajc, A. Trost: Zbornik triindvajsete mednarodne Elektrotehniške in računalniške konference ERK 2014, 22. - 24. September 2014, Portorož, Slovenija

>>>>

Robotic manipulators, specifically those with a high degree of freedom (DOF), possess a crucial characteristic known as kinematic redundancy~\cite{Nguyen1991}. Kinematic redundancy refers to having more joints (i.e., degrees of freedom - DOF) than required to perform a task, thus allowing the robot to adopt multiple configurations to accomplish the same end-effector position and orientation. This redundancy provides a considerable advantage, making it possible for manipulators to optimize movement according to different criteria, such as energy efficiency, obstacle avoidance, or joint limit avoidance.

@@

Geometric kinematics (also known as forward and inverse kinematics) focuses on the relationship between joint angles and the position and orientation of the end-effector. Forward kinematics involves calculating the position and orientation of the end-effector given the joint angles, while inverse kinematics is the process of determining the joint angles for a desired end-effector position and orientation. In the case or redundant manipulator, there isn't an unique mapping from EE coordinates to the joint coordinates as there exist an infinite number of different joint angles configurations that map to the same EE position.

Differential kinematics, also known as the robots Jacobian, forms the foundation of robot velocity analysis. The Jacobian matrix, often represented as $J$, encapsulates the relationship between the joint velocities and the end-effector linear and angular velocities. It's derived from the partial derivatives of the forward kinematics.

@@

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{kernel-mainvalues-colored.png}
	\caption{The kernel values along the primary axis exhibit a pattern of symmetrical distribution with negative polarity on one side.} 
	\label{Kernel main axis}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\linewidth]{kernel-matrix.png}
	\caption{In most instances, an equal width and height around the primary axis are desired, creating a symmetrical detection area.} 
	\label{Kernel matrix}
\end{figure}

\todocomment{while not the most important fix, currently values in matrix don't follow values used in experiments}

@@

\bibitem{Nguyen1991} Nguyen, Charles C., Zhou, Zhen-Lei, Mosier, Gary E. (1991) Analysis and control of a kinematically redundant manipulator. \textit{Computers \& Electrical Engineering}, 17(3), pp. 147–161. doi:10.1016/0045-7906(91)90031-T.
\bibitem{ERK} ERK, http://www.ieee.si/erk/index.html 
\bibitem{Zbornik} B. Zajc, A. Trost: Zbornik triindvajsete mednarodne Elektrotehniške in računalniške konference ERK 2014, 22. - 24. September 2014, Portorož, Slovenija
